Plotting plots and Hotzenplotz

### 2024-11-11 draftdata.Rmd
pushrestructuresubmenudata

            -   From Lucan: "The h-index namely measures an author’s prestige by calculating the number of publications that have been cited at least as many times as the total number of their publications. As explained by the creator of the h-index, ” A scientist has index h if h of his or her Np papers have at least h citations each and the other (Np - h) papers have ≤h citations each” (@Hirsch2005) "

@@

```{=html}
<!-- -->
```
-   Code for this was provided by a fellow course mate, namely Lucan Bovens

@@

    -   "SIENA, shorthand for **Simulation Investigation for Empirical Network Analysis**, is a computer program that carries out the statistical estimation of models for repeated measures of social networks according to the dynamic actor-oriented model of Snijders and van Duijn (1997), Snijders (2001), and Snijders, Steglich, and Schweinberger (2007); also see Steglich, Snijders, and Pearson (2009). A tutorial for these models is in Snijders, van de Bunt, and Steglich (2009). Some examples are presented, e.g., in van de Bunt (1999); van de Bunt, van Duijn, and Snijders (1999); and van Duijn, Zeggelink, Stokman, and Wasseur (2003); and Steglich, Snijders, and West (2006). A website for SIENA is maintained at http://www.stats.ox.ac.uk/\~snijders/siena/ . At this website (‘publications’ tab) you shall also find references to introductions in various other languages.
        This is a provisional manual for SIENA version 4.0, which is also called RSiena. This is a contributed package for the R statistical system which can be downloaded from http://cran.r-project.org. For the operation of R, the reader is referred to the corresponding manual. If desired, SIENA can be operated apparently independently of R, as is explained in Section 2.1.
        RSiena was programmed by Ruth Ripley and Krists Boitmanis, in collaboration with Tom Snijders."

>>>>

        ```         
        -   From Lucan: "The h-index namely measures an author’s prestige by calculating the number of publications that have been cited at least as many times as the total number of their publications. As explained by the creator of the h-index, ” A scientist has index h if h of his or her Np papers have at least h citations each and the other (Np - h) papers have ≤h citations each” (@Hirsch2005) "
        ```

@@

<!-- -->

-   Code for this was provided by a fellow course mate, namely Lucan Bovens

@@

    -   "SIENA, shorthand for **Simulation Investigation for Empirical Network Analysis**, is a computer program that carries out the statistical estimation of models for repeated measures of social networks according to the dynamic actor-oriented model of Snijders and van Duijn (1997), Snijders (2001), and Snijders, Steglich, and Schweinberger (2007); also see Steglich, Snijders, and Pearson (2009). A tutorial for these models is in Snijders, van de Bunt, and Steglich (2009). Some examples are presented, e.g., in van de Bunt (1999); van de Bunt, van Duijn, and Snijders (1999); and van Duijn, Zeggelink, Stokman, and Wasseur (2003); and Steglich, Snijders, and West (2006). A website for SIENA is maintained at [http://www.stats.ox.ac.uk/\\\~snijders/siena/](http://www.stats.ox.ac.uk/\~snijders/siena/){.uri} . At this website (‘publications’ tab) you shall also find references to introductions in various other languages. This is a provisional manual for SIENA version 4.0, which is also called RSiena. This is a contributed package for the R statistical system which can be downloaded from <http://cran.r-project.org>. For the operation of R, the reader is referred to the corresponding manual. If desired, SIENA can be operated apparently independently of R, as is explained in Section 2.1. RSiena was programmed by Ruth Ripley and Krists Boitmanis, in collaboration with Tom Snijders."

### 2024-11-11 revisitwithJochem.Rmd
pushrestructuresubmenudata

```{r RSiena}
#step1 data
wave1 <- test$nets[1,,]
wave2 <- test$nets[2,,]

@@

```{r RSiena2}
# put the nets in an array
net_array <- array(data = c(wave1, wave2), dim = c(dim(wave1), 2))
#dependent
nets <- sienaDependent(net_array)

@@

```{r RSiena-model estimate}
# estimate the model 
model1 <- siena07(myAlgorithm, data = mydata, effects = myeff, returnDeps = TRUE)
#latter needed for GOF

model1

>>>>

## Step 1: Define data
```{r RSiena}
#step1 data
wave1 <- test$nets[1,,]
wave2 <- test$nets[2,,]

@@

```{r RSiena define}
# put the nets in an array
net_array <- array(data = c(wave1, wave2), dim = c(dim(wave1), 2))
#dependent
nets <- sienaDependent(net_array)

@@

## Step 5: Estimate model 
```{r RSiena-model estimate}
# estimate the model 
model1 <- siena07(myAlgorithm, data = mydata, effects = myeff, returnDeps = TRUE)
#latter needed for GOF

# model1   #remove the comment to run model!!!!!
